\chapter[Background]{Background}

This thesis is built up using many backgrounds on memory management, the
Windows internals and some malware prevention technology. This chapter will
give readers a quick summary to understand these key points. The chapter
heavily depends on these materials \cite{ligh2014art}
\cite{russinovich2012windows}.

\input{chapters/background/1.pagination.tex}
\input{chapters/background/2.windows.tex}
\input{chapters/background/4.counter.tex}

\chapter[Hidden malware and memory forensics]{Hidden malware and memory forensics}

Malware has many ways to run inside the system. It can create a process, create
a thread, load a library, or run a driver. A hidden malware will make these
objects can not be found when using Windows API or by traversing the legacy
lists.  For example, there are Windows APIs that can get information on
processes, threads, libraries, drivers, \texttt{EnumProcesses},
\texttt{Thread32First}, \texttt{EnumDeviceDrivers},
\texttt{NtQuerySystemInformation}. Malware will try to remove itself from these
API results. Thus, if an inspection system uses these API, the malware present
is not shown. To reveal the malware, one has to use forensics methods,
including but not limited to memory forensics.  In this chapter, we present in
technical terms how malware interfere with the system in order to hide and how
forensics investigators can find them using memory forensics.

\input{chapters/background/3.hiding.tex}
\input{chapters/background/5.forensics.tex}
