\chapter[Introduction]{Introduction}

\section[Motivation]{Motivation}

Throughout the years of computer development, computers have become a standard
method for humans around the world to study, work and entertain. Most
activities of our daily lives involve computers. Individuals across the globe
have created systems running on computers to assist them in doing common and
complex tasks. However, this somehow influenced other people to commit harmful
activities, these people often refer to as \textit{hacker}. Hackers have been
creating software to cause damage and steal confidential or private
information, these software are malware. Furthermore, lately along with the
trend of cryptocurrency, while ordinary people commit their investment by using
crypto mining machines, hackers, on the other hand, create sophisticated
software (cryptojacking malware) that stealthily installed on a victim machine
and mine cryptocurrency without the victim's acknowledgement.

Security researchers have been struggling to find ways to mitigate the gaining
rate of attacks. However, it was never close to perfection. Security
researchers uses file checksum and unique bytes sequences in file to create a
file signature and combines a list of malware signature to a database, for
example yararules \cite{yararules}. Relying on file signature database for
filtering file often miss out new one, thus, it is highly vulnerable to the
newer class of malware. To counterattack these new malware when an attack
happens, digital forensics is performed. Digital forensics which as described
by The Forensics Research Workshop I \cite{roadmap}:

\say{The use of scientifically derived and proven methods toward the
preservation, collection, validation, identification, analysis, interpretation,
documentation and presentation of digital evidence derived from digital sources
for the purpose of facilitating or furthering the reconstruction of events
found to be criminal, or helping to anticipate unauthorized actions shown to be
disruptive to planned operations.}

Digital forensics includes many different aspects, however, the most intrigued
part of digital forensics is memory forensics, which ``provides unprecedented
visibility into the runtime state of the system, such as which processes were
running, open network connections, and recently executed commands'' as stated
in the book The Art of Memory Forensics \cite{ligh2014art}. Memory forensics
provide a frame of the computer state, from which one can extract files and
processes. Researchers often extract suspicious files from these memory
samples, then reverse engineer it, if the file is a malware, they will create
the file signature and add to the database. Digital forensics and memory
forensics is very important to gain insight on the cyber attacks made by
hackers. However, prevention is always better than fixing, and with the rise of
the more steathy malware, the computer security industry is facing a major
problem.

Software will not be considered as malware until they are found doing malicious
behaviours. Therefore hackers create malware hidden from the Task Manager and
other process listing tools. From the early days of 1990s, they have been
improving ways to hide malware. In 2017, a small report \cite{evolutionHidding}
have revised on hiding techniques used by malware over the years in the Windows
OS. Most of these techniques is either preventable or mitigable. However, even
in 2019, we can still observe incidences where malware hide itself so
effectively. For example, the \textit{Titanium} backdoor\footnote{Programs that
receives remote connections} on Windows 10 disclosed November 2019
\cite{titanium}. Security researchers collected and analyzed these malware, but
a normal user would not be able to do that. For a normal user, if the
anti-virus software failed to flag the file as mallicious, suspect's computer
will be infected. To know whether a system is having a hidden malware running,
one must send an investigator a memory extraction. Such process is complex,
long and costly, a user must know how to extract the memory and hire an
investigator to analyze. If there were a tool to do memory forensics live,
while the system is running, and extract the hidden malware automatically, it
would be easier for a normal user. Looking in live memory forensics, Shuaibur
Rahman and Khan \cite{reviewLive} has a review of live forensics analysis
techniques in 2015, and in the review there is one work that can extract
running, finished, and cached processes \cite{comparativeLive}. However, the
work is only restricted to the Linux OS and requires an experienced
investigator to do. Besides that, there are projects that implements memory
forensics techniques but is limited to dump file analysis. We have researched
for live memory analysis and have come up with a method for finding hidden
processes.

Within the scope of the thesis, we will create a tool finding hidden processes
aims at normal users. The tool could also submit the binary along with the
process memory to the remote server. And with the market share of Windows over
others OS is more than 75\% \cite{osMarketShare}, within the Windows OS,
version 10 is now dominating with more than 60\% \cite{windowsShare}, this tool
will focus on Windows 10 live memory analysis.

\section[Objectives]{Objectives}

In the scope of this thesis, we wish to:

\begin{itemize}
% \setlength\itemsep{-0.5em}
  \item Understand the basics concept of OS that supports memory forensics,
  \item Understand to some extent of Windows internals,
  \item Understand some techniques often used to do Windows memory forensics,
  \item Analyze some already existed tools doing memory forensics,
  \item Propose a method to find hidden running processes in a running Windows machine,
  \item Implement the method in a demonstrating version and perform evaluation.
\end{itemize}

\newpage
\section[Structure]{Structure}

\begin{itemize}
  \item Chapter 1 gives an overview, the goals and challenges of this thesis proposal,
  \item Chapter 2 presents the background on OS, Windows Internal and Digital forensics techniques,
  \item Chapter 3 introduces some products doing digital forensics,
  \item Chapter 4 suggests a method to perform live memory forensics on Windows 10,
  \item Chapter 5 states some challenges the proposed method might encounter and gives directions for implementation.
\end{itemize}

\section[Timeline]{Timeline}

In the next stage of the thesis, we will finish the followings works:

\begin{itemize}
  \item January to Feburary 2019: Implementation of the tool base on proposed method,
  \item March 2019: Perform testing on Windows 10 and older version,
  \item April 2019: Resolve the addressed challenges.
\end{itemize}
